Do educational institutions explain SES gaps?: an interntational comparison of the SES achievement gap from 2000-2015

### 2017-10-06 paper/paper.Rnw
Remove PISA2012 packae because wasn't used

<<default_conf>>=
  library(matrixStats)
  library(knitr)
  library(arm)
  library(saves)
  library(haven)
  library(PISA2000lite)
  library(PISA2003lite)
  library(PISA2006lite)
  library(PISA2009lite)
  library(PISA2012lite)
  library(intsvy)
  library(cimentadaj) # devtools::install_github("cimentadaj/cimentadaj")
  library(countrycode) # For region variable
  library(car)
  library(SAScii)
  library(inequalityintsvy) # devtools::install_github("cimentadaj/inequalityintsvy")
  library(lme4)
  library(modelr)
  library(ggrepel)
  library(xtable)
  library(ggthemes)
  library(readxl)
  library(inequalityintsvy)
  library(brms)
  library(tidyverse)

>>>>

<<default_conf>>=
  library(matrixStats)
  library(knitr)
  library(arm)
  library(saves)
  library(haven)
  library(PISA2000lite)
  library(PISA2003lite)
  library(PISA2006lite)
  library(PISA2009lite)
  library(intsvy)
  library(cimentadaj) # devtools::install_github("cimentadaj/cimentadaj")
  library(countrycode) # For region variable
  library(car)
  library(SAScii)
  library(inequalityintsvy) # devtools::install_github("cimentadaj/inequalityintsvy")
  library(lme4)
  library(modelr)
  library(ggrepel)
  library(xtable)
  library(ggthemes)
  library(readxl)
  library(inequalityintsvy)
  library(brms)
  library(tidyverse)
